---
title: "HW 5"
author: "Elaine Xu"
date: "11/14/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r, warning=FALSE, message=FALSE}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r, warning=FALSE, message=FALSE}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



## Problem 2


Import one dataset 

```{r, message=FALSE}
path_df = 
  tibble(
    path = list.files("./data"),
  ) %>% 
  mutate(
    path = str_c("./data/", path),
    data = map(.x = path,~read_csv(.x)),
    arm = str_remove(path, ".csv"),
    arm = str_remove(arm, "./data/")) %>%
   separate(arm,c("arm","id"),sep = "_")%>%
  mutate(
    arm = ifelse(arm == "con", "control", "experiment")
  ) %>%
  unnest(data) %>%
  pivot_longer(
    week_1:week_8,
    values_to = "observation",
    names_to = "week"
  ) %>%
  mutate(week = str_remove(week, "week_")) %>%
  select(-path)

path_df
```

Spaghetti plot

```{r}
spaghetti = path_df %>%
  mutate(arm_new = arm) %>%
  unite("subjects", c(arm, id))
  

ggplot()+geom_line(data = spaghetti, aes(x = week, y = observation, group = subjects, color = arm_new))+
  labs(title="observations on each subject over time")

```

From the graph, we can see that experiment groups have increased through the eight weeks, and it's overall observation values are higher than control groups. Control groups' trends didn't have a very significant increase or decrease through these eight weeks.


## Problem 3

Function for t-test
```{r}

set.seed(33)

# n = 30
# sigma = 5

ttest = function(mu) {
  
  sim_data = tibble(
    x = rnorm(n = 30, mean = mu, sd = 5),
  )
  
  sim_data %>% 
    summarize(
      t.test(x, mu = 0, conf.level = 0.95) %>%
    broom::tidy() )
}

```

generate 5000 datasets and repeat
```{r, message=FALSE}

com_result = function(mu){
  
  rerun(5000, ttest(mu)) %>%
    bind_rows() %>%
    select(p.value, estimate)
}

# for mu = 0
com_result(0)

# for mu = 1,2,3,4,5,6

mu_result = tibble(
  mu = c(0,1,2,3,4,5,6)
) %>%
  mutate(output = map(.x = mu, ~com_result(.x))) %>%
  unnest(output) %>%
  select(mu, p.value)
```

plot showing the proportion of times the null was rejected and true mean
```{r, message=FALSE}
porp_test = mu_result %>%
  group_by(mu) %>%
  filter(p.value < 0.05) %>%
  summarize(
    reject = n(),
    reject = reject/5000
  )

ggplot(data = porp_test, aes(x = mu, y = reject, color = mu)) + geom_line() + geom_point() +
  scale_x_continuous(limits = c(0,6), breaks = seq(0,6,1)) +
  labs(
    x = "true mean",
    y = "Proportion of times the null was rejected"
  )
```

__From the plot above we can see that when the mu is increasing, the power also increases. When true mean gets larger, the proportion of the null (mu = 0) was rejected also gets larger and approaching to 1.__


plot showing the average estimate of mu hat on the y axis and the true value of mu on the x axis.
```{r, message=FALSE}
ave_estimate = tibble(
  mu = c(0,1,2,3,4,5,6)
) %>%
  mutate(output = map(.x = mu, ~com_result(.x))) %>%
  unnest(output) %>%
  group_by(mu) %>%
  summarize(
    estimate = mean(estimate)
  )

ggplot(data = ave_estimate, aes(x = mu, y = estimate, color = mu)) + geom_line() + geom_point() +
  scale_x_continuous(limits = c(0,6), breaks = seq(0,6,1)) +
  labs(
    x = "true mean",
    y = "average estimate of mu hat"
  )
  
```


plot the average estimate of mu hat only in samples for which the null was rejected on the y axis and the true value of mu on the x axis.

```{r, message=FALSE}
sam_estimate = tibble(
  mu = c(0,1,2,3,4,5,6)
) %>%
  mutate(output = map(.x = mu, ~com_result(.x))) %>%
  unnest(output) %>%
  select(mu, p.value, estimate) %>%
group_by(mu) %>%
  filter(p.value < 0.05) %>%
  summarize(
    estimate = mean(estimate)
  )

ggplot(data = sam_estimate, aes(x = mu, y = estimate, color = mu)) + geom_line() + geom_point() +
  scale_x_continuous(limits = c(0,6), breaks = seq(0,6,1)) +
  labs(
    x = "true mean",
    y = "average estimate of mu hat",
    title = " average estimate of mu hat only in samples for which the null was rejected"
  )
```

__For mu = 0, 1, 2,  we can see that the sample average mu hat for which the null is rejected is different with the true mean. When mu increases (mu = 3, 4, 5, 6), the sample average mu hat is getting closer and closer to the true mean, which is approximately equal to the true mean. This is because when true mean increases, the probability that the null hypothesis rejected also increases.__



