---
title: "HW 5"
author: "Elaine Xu"
date: "11/14/2020"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r, warning=FALSE, message=FALSE}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r, warning=FALSE, message=FALSE}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



## Problem 2


Import one dataset 

```{r, message=FALSE}
path_df = 
  tibble(
    path = list.files("./data"),
  ) %>% 
  mutate(
    path = str_c("./data/", path),
    data = map(.x = path,~read_csv(.x)),
    arm = str_remove(path, ".csv"),
    arm = str_remove(arm, "./data/")) %>%
   separate(arm,c("arm","id"),sep = "_")%>%
  mutate(
    arm = ifelse(arm == "con", "control", "experiment")
  ) %>%
  unnest(data) %>%
  pivot_longer(
    week_1:week_8,
    values_to = "observation",
    names_to = "week"
  ) %>%
  mutate(week = str_remove(week, "week_")) %>%
  select(-path)

path_df
```

Spaghetti plot

```{r}
spaghetti = path_df %>%
  mutate(arm_new = arm) %>%
  unite("subjects", c(arm, id))
  

ggplot()+geom_line(data = spaghetti, aes(x = week, y = observation, group = subjects, color = arm_new))+
  labs(title="observations on each subject over time")

```

From the graph, we can see that experiment groups have increased through the eight weeks, and it's overall observation values are higher than control groups. Control groups' trends didn't have a very significant increase or decrease through these eight weeks.


## Problem 3

Function for t-test
```{r}

set.seed(100)

n = 30
sigma = 5

ttest = function(mu) {
  
  sim_data = tibble(
    x = rnorm(n = 30, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      t_test = t.test(x, mu = mu, conf.level = 0.95)%>%
    broom::tidy() %>%
    select(p.value))
}

```

generate 5000 datasets and repeat
```{r, message=FALSE}

com_result = function(mu){
  
  rerun(5000, ttest(mu)) %>%
    bind_rows() %>% 
  mutate(p_value = t_test$p.value) %>% 
  select(mu_hat, p_value)
}

# for mu = 0
com_result(0)

# for mu = 1,2,3,4,5,6

mu_result = tibble(
  mu = c(0,1,2,3,4,5,6)
) %>%
  mutate(output = map(.x = mu, ~com_result(.x)),
         estimate = map(output, bind_rows)) %>%
  unnest(estimate) %>%
  select(mu, mu_hat, p_value)

mu_result


#plot showing the proportion of times the null was rejected and true mean

porp_test = mu_result %>%
  filter(p_value<0.05) %>%
  group_by(mu) %>%
  summarize(
    reject = n()
  ) %>%
  mutate(porp = reject/5000)

ggplot(data = porp_test, aes(x = mu, y = porp)) + geom_line() +
  labs(
    x = "true mean",
    y = "Proportion of times the null was rejected"
  )
```




